# Missing data, outliers, and checking assumptions

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE, 
                      echo = TRUE)

```

```{r echo=FALSE}
library(effectsize)
library(performance)
library(tidyverse)
```

In this chapter...

**Chapter Intended Learning Outcomes (ILOs)**

By the end of this chapter, you will be able to: 

- ILO1. 

## Chapter preparation

### Organising your files and project for the chapter

For this chapter, we are going to revisit the data sets you worked with in Chapters 8 [@dawtry_why_2015] and 9 [@lopez_visual_2023]. They each presented some useful examples for checking statistical assumptions and the decisions that go into data analysis. We might not use both data sets for each topic we cover, but they will be useful to demonstrate some of the problems and decisions we highlighted in previous chapters, but did not explore solutions.

Before we can get started, you need to organise your files and project for the chapter, so your working directory is in order.

1. In your folder for research methods and the book `ResearchMethods1_2/Quant_Fundamentals`, create a new folder called `Chapter_11_screening_data`. Within `CChapter_11_screening_data`, create two new folders called `data` and `figures`.

2. Create an R Project for `Chapter_11_screening_data` as an existing directory for your chapter folder. This should now be your working directory.

3. Create a new R Markdown document and give it a sensible title describing the chapter, such as `11 Missing Data, Outliers, and Assumptions`. Delete everything below line 10 so you have a blank file to work with and save the file in your `Chapter_11_screening_data` folder. 

4. The @dawtry_why_2015 data wrangling steps were quite long, so please save this clean version of the data to focus on screening data in this chapter: [Dawtry_2015_clean.csv](data/Dawtry_2015_clean.csv). You will also need to save the data from @lopez_visual_2023 if you have not downloaded it yet: [Lopez_2023.csv](data/Lopez_2023.csv). Right click the link and select "save link as", or clicking the link will save the files to your Downloads. Make sure that you save the files as ".csv". Save or copy the files to your `data/` folder within `Chapter_11_screening_data`.

You are now ready to start working on the chapter! 

### Activity 1 - Read and wrangle the data

As the first activity, try and test yourself by completing the following task list to read and wrangle the two data files. There is nothing extra to do with this version of the Dawtry data and one small step for the Lopez data. 

::: {.callout-tip}
#### Try this

To read and wrangle the data, complete the following tasks: 

1. Load the following packages:

    - <pkg>performance</pkg>
    
    - <pkg>tidyverse</pkg>

2. Read the data file `data/Dawtry_2015_clean.csv` to the object name `dawtry_clean`.

2. Read the data file `data/Lopez_2023.csv` to the object name `lopez_data`.

3. Create a new object called `lopez_clean` based on `lopez_data`:

    - Create a new variable called `Condition_label` by recoding `Condition`. "0" is the "Control" group and "1" is the "Experimental" group. 

:::

::: {.callout-caution collapse="true"}
#### Show me the solution
You should have the following in a code chunk: 

```{r eval=FALSE}
# load the relevant packages
library(performance)
library(tidyverse)

# Read the Dawtry_2015_clean.csv file 
dawtry_clean <- read_csv("data/Dawtry_2015_clean.csv")

# Read the Lopez_2023.csv file 
lopez_data <- read_csv("data/Lopez_2023.csv")

# recode condition
lopez_clean <- lopez_data %>% 
  mutate(Condition_label = case_match(Condition,
                                      0 ~ "Control",
                                      1 ~ "Experimental"))
```

:::

## Missing data

## Outliers

## Checking assumptions

## Test yourself

To end the chapter, we have some knowledge check questions to test your understanding of the concepts we covered in the chapter. We then have some error mode tasks to see if you can find the solution to some common errors in the concepts we covered in this chapter. 

### Knowledge check

**Question 1**.

### Error mode

The following questions are designed to introduce you to making and fixing errors. For this topic, we focus on the new types of data visualisation. Remember to keep a note of what kind of error messages you receive and how you fixed them, so you have a bank of solutions when you tackle errors independently. 

Create and save a new R Markdown file for these activities. Delete the example code, so your file is blank from line 10.

...

## Words from this Chapter

Below you will find a list of words that were used in this chapter that might be new to you in case it helps to have somewhere to refer back to what they mean. The links in this table take you to the entry for the words in the [PsyTeachR Glossary](https://psyteachr.github.io/glossary/){target="_blank"}. Note that the Glossary is written by numerous members of the team and as such may use slightly different terminology from that shown in the chapter.

```{r gloss, echo=FALSE, results='asis'}
glossary_table()
```

## End of Chapter

That is the final chapter you will complete for Research Methods 1. 

